---
title: "Computers and jobs - Imports data"
author: "Bruno Azuma Balzano"
format:
  gfm:
    df-print: kable
editor: visual
---

In order to have some variable about the usage of computers for professional reasons, I'll get data about imports of HS 8471 products. I do that because specific data on computer usage is not available annually, so I use import data on the

# Setup

As always, I'll start by setting up the libraries and configurations needed to run the entire notebook.

```{r}
setwd("D:/OneDrive/R Workspace/computers_and_jobs")
library("dotenv")
library("arrow")
library("tidyverse")
library("basedosdados")
library("bigrquery")
```

First, I need to setup the GCP project data for using the \`basedosdados\` package to get the data.

```{r}
load_dot_env()

project_id <- Sys.getenv("GCP_PROJECT_ID")

set_billing_id(project_id)

bq_auth(email = Sys.getenv("GCP_EMAIL"))
```

```{r}
peek <- basedosdados::read_sql("SELECT * FROM `basedosdados.br_me_comex_stat.municipio_importacao` LIMIT 1")
peek %>% dplyr::glimpse()
```

# Download from BigQuery

Now, I download the Comex Stat data from basedosdados.

```{r}
sql <- "
SELECT
  imp.ano,
  imp.sigla_uf,
  imp.id_sh4,
  SUM(imp.peso_liquido_kg) AS peso_liquido_kg,
  SUM(imp.valor_fob_dolar) AS valor_fob_dolar
FROM
  `basedosdados.br_me_comex_stat.municipio_importacao` AS imp
WHERE
  imp.ano > 2005
  AND
  imp.ano < 2022
  AND
  imp.id_sh4 = '8471'
GROUP BY
  imp.ano,
  imp.sigla_uf,
  imp.id_sh4;
"

imports <- basedosdados::read_sql(sql)
imports %>% head()
```

# Saving to parquet

As nothing seems to be wrong with the dataset, I save it as a parquet file.

```{r}
data_dir <- "data/"
file <- str_interp("${data_dir}Imports.parquet")

write_parquet(imports, file)
```
